### 2020-04-03 readme.Rmd
Add https cran link

[![Build Status](https://travis-ci.org/lebebr01/highlightHTML.svg?branch=master)](https://travis-ci.org/lebebr01/highlightHTML)
[![codecov.io](https://codecov.io/github/lebebr01/highlightHTML/coverage.svg?branch=master)](https://codecov.io/github/lebebr01/highlightHTML?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](http://cran.r-project.org/package=highlightHTML)

>>>>

[![Build Status](https://travis-ci.org/lebebr01/highlightHTML.svg?branch=master)](https://travis-ci.org/lebebr01/highlightHTML)
[![R build status](https://github.com/lebebr01/highlightHTML/workflows/R-CMD-check/badge.svg)](https://github.com/lebebr01/highlightHTML/actions?workflow=R-CMD-check)
[![codecov.io](https://codecov.io/github/lebebr01/highlightHTML/coverage.svg?branch=master)](https://codecov.io/github/lebebr01/highlightHTML?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/highlightHTML)](https://cran.r-project.org/package=highlightHTML)
[![DOI](http://joss.theoj.org/papers/10.21105/joss.00185/status.svg)](https://doi.org/10.21105/joss.00185)
